---
title: "Social frontiers Pardubice"
author: "Meng Le Zhang"
date: "13 August 2018"
output:
  html_document:
    toc: yes
    toc_float: yes
  word_document:
    toc: yes
always_allow_html: yes
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = F)

## Load packages and data
library(tidyverse)
library(sf)
library(tmap)
library(stargazer)

tmap_mode('plot')

##  Frontier data
res.frontier1 <- readRDS('./Results/London frontiers all results A.RDS')

```

## Introduction

This is the analysis of social frontiers in Pardubice and the relationship 
between crimes and frontiers. We use proportion of foreigners in 2011 and exclude
Basic Settlement Units (BSUs) with less than 10 people residing in them. This is
to exclude non-residential zones from the analysis (e.g. Pardubice hospital).

### Frontiers using all types of foreigners 

This gives us a total of 
`r res.frontier1$data %>% nrow` 
BSUs in our dataset.
First we look at statistically significant with a substantial difference in 
proportions of all foreginers. This results in 
`r res.frontier1$frontier.sf %>%subset(sig.frontier == T) %>% nrow`
borders between BSUs classified as social frontiers (out of a possible 
`r res.frontier1$frontier.sf %>% nrow`
borders). The table below gives summary statistics comparing the absolute difference
in crime between frontiers and non-frontiers. The p-value of the permutation test
is 
`r res.frontier1$pval %>% round(3)`.

```{r tab1}
aggregate(crime.diff ~ sig.frontier, data = res.frontier1$frontier.sf, summary) 

```

A map of social frontiers and proportion of non-UK-born is given below. 

```{r fig1}
tmap_mode('plot')

tm_shape(res.frontier1$data) +
  tm_fill('prop.foreign', alpha = 0.6, 
          palette = 'BrBG' 
          #style = 'cont',
          #breaks = c(0, 0.1, 0.2, 0.3, 1
                     ) +
qtm(res.frontier1$frontier.gfx %>% subset(sig.frontier == T)) +
  tm_scale_bar(position = c('center', 'bottom')) +
  tm_layout(title = 'Proportion non-UK-born and social frontiers') 

# tm_shape(res.frontier1$data) +
#   tm_fill('Prop_crimes_km2', alpha = 0.6, 
#           palette = 'Reds', 
#           style = 'quantile',
#           ) +
# qtm(res.frontier1$frontier.gfx %>% subset(sig.frontier == T)) +
#   tm_scale_bar(position = c('center', 'bottom')) +
#   tm_layout(title = 'Crime rate and social frontiers') 

```

